---
title: "Plotly_Visualization"
author: "Dhaval Mandalia"
date: "January 10, 2019"
output: slidy_presentation
#html_document
#ioslides_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(rgl.printRglwidget = TRUE)
```

## First Plotly Visualization
Simple cars dataframe used to scatter plot weight vs miles per gallon data.

```{r FirstStep, echo=FALSE, message=FALSE}
library(plotly)
plot_ly(mtcars,x=~wt,y=~mpg,mode="markers")
```

## Second Step to utilize other Plotly options

```{r SecondStep, echo=FALSE, message=FALSE, warning=FALSE}
#plot_ly(mtcars,x=~wt,y=~mpg,mode="markers",color = ~as.factor(cyl))
#plot_ly(mtcars,x=~wt,y=~mpg,mode="markers",color = ~disp)
plot_ly(mtcars,x=~wt,y=~mpg,mode="markers",color = ~as.factor(cyl),size=~hp*100)

```

## Third step to create 3D Scatter Plot

```{r ThirdStep, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(101)
plot_ly(mtcars,x=~wt,y=~mpg, z=~carb,type="scatter3d",mode="markers",color = ~as.factor(cyl))

```

## Fourth Step on Line Charts

```{r FourthStep, echo=FALSE, warning=FALSE}
library(dplyr);library(tidyr)
data("EuStockMarkets")

stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index,price) %>%
  mutate(time = rep(time(EuStockMarkets),4))

plot_ly(stocks,x=~time,y=~price,color = ~index)

```


## Fifth Step to look at other types of charts

```{r FifthStep, echo=FALSE, warning=FALSE}
precip <- rnorm(100)
print("Sample Histogram:")
plot_ly(x=precip,type="histogram")
print("Sample Boxplot:")
plot_ly(iris,y=~Petal.Length,color=~Species,type="box")
print("Sample Heatmap:")
terrain <-matrix(rnorm(100*100),nrow=100,ncol=100)
plot_ly(z=terrain,type="heatmap")
print("Sample Surface:")
terrain1 <-matrix(sort(rnorm(100*100)),nrow=100,ncol=100)
plot_ly(z=terrain1,type="surface")
```


## Sixth Step to look at other types of charts

```{r SixthStep, echo=FALSE, warning=FALSE}
##Choropleth Maps
state_pop <- data.frame(State = state.abb,Pop=as.vector(state.x77[,1]))
state_pop$hover <- with(state_pop,paste(State,'<br>',"Population:",Pop))
borders <- list(color = toRGB("red"))
map_options <- list(scope='usa',projection=list(type = 'albers usa'), showlakes = TRUE,lakecolr = toRGB('white'))

plot_ly(state_pop,z=~Pop,text=~hover,locations=~State ,type='choropleth',locationmode='USA-states',color=~Pop,colors='Blues',marker=list(line=borders)) %>%
  layout(title='US Population in 1975',geo=map_options)

```

## Thank You !!!